---
title: "Untitled"
author: "RN7"
date: "February 2, 2019"
always_allow_html: yes
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```

> "Hey there criminal. It's me, Johnny Law!" - Jake Peralta, NYPD.

_Brooklyn Nine-Nine_ has become one of my favorite sitcoms in recent years, probably taking over from Parks & Recreation and Community. So in this blog post, I'm going to web scrape some very simple TV statistics, clean it up with the `tidyverse`, and visualize it with `ggplot2`... 

__"Terry loves ggplot2!"__

Let's get started!

# Packages

```{r warning=FALSE, message=FALSE}
pacman::p_load(tidyverse, rvest, glue, cowplot, ggbeeswarm, gt,
               polite, extrafont, scales, gridExtra, knitr, kableExtra)
loadfonts() # "Univers" and "Univers LT 93 ExtraBlackEx" fonts
```

# B99 Custom Theme

First, I will create a custom _Brooklyn Nine-Nine_ theme that I can put on every plot that I will create. This will save me time from typing in the same options over and over again! I googled the font type that the official _Brooklyn Nine-Nine_ media uses, downloaded them, and got it installed for R using the `extrafont` package. For some of the different colors you'll see in the plots I sourced them from pasting in the _Brooklyn Nine-Nine_ logo and other official media images into [imagecolorpicker.com](https://imagecolorpicker.com/en) and saving the hex codes that it gave me. Otherwise, I experimented with different palettes from perusing [Emil Hvitfeld's](https://twitter.com/Emil_Hvitfeldt/) awesome [r-color-palettes](https://github.com/EmilHvitfeldt/r-color-palettes) Github repository (Also special thanks to [David Smale](https://twitter.com/committedtotape) for giving me some advice on using color!).

```{r}
theme_b99 <- function(){
  
  base_size <- 11
  half_line <- base_size / 2
  
  theme_minimal() %+replace%
    theme(text = element_text(family = "Univers", color = "#F9FEFF",
                              face = "plain", size = 14, 
                              hjust = 0.5, vjust = 0.5, angle = 0,
                              lineheight = 0.9, 
                              margin = margin(half_line, half_line,
                                              half_line, half_line),
                              debug = FALSE),
          plot.title = element_text(family = "Univers LT 93 ExtraBlackEx",
                                    size = 20, color = "#F9FEFF"),
          plot.background = element_rect(color = NA, fill = "#0053CD"), 
          panel.background = element_rect(color = NA, fill = "#0053CD"),
          # axis options
          axis.text = element_text(family = "Univers", color = "#F9FEFF", size = 12),
          axis.title = element_text(size = 14),
          # legend options (for ratings plot)
          legend.title = element_text(family = "Univers", color = "#F9FEFF"),
          legend.text = element_text(family = "Univers", color = "#F9FEFF",
                                     size = 9),
          legend.position = "bottom",
          legend.key = element_rect(colour = "black", linetype = "solid", size = 1.5),
          legend.background = element_rect(color = "black", fill = "#0053CD",
                                           linetype = "solid"))
}
```

Now the plots will all look very similar like a good police squad should:

<center>
<img src = "https://media3.giphy.com/media/3oxHQoyto7T8wBjUJ2/giphy.gif" width = "450" />
</center>

With that done, I can start making plots!

# Episode Ratings

As in my more [recent](https://ryo-n7.github.io/2019-01-11-visualize-asian-cup/) blog posts I will use the `polite` package to web scrape responsibly (note the `bow()` and `scrape()` functions).

I `map_2()` over the IMDB page for the episodes for each season and I append the season number to each episode row. After I'm done with the web scraping I `mutate()` in the episode number for each season.

```{r, message=FALSE, warning=FALSE}
url_df <- tibble(
  urls = c("https://www.imdb.com/title/tt2467372/episodes?season=1",
           "https://www.imdb.com/title/tt2467372/episodes?season=2",
           "https://www.imdb.com/title/tt2467372/episodes?season=3",
           "https://www.imdb.com/title/tt2467372/episodes?season=4",
           "https://www.imdb.com/title/tt2467372/episodes?season=5"),
  season_num = c(1, 2, 3, 4, 5)) 

# scraping function:
brooklyn99_ep_rating <- function(url) {
  
  session <- bow(url)
  url2 <- scrape(session)
  
  # Grab episode names
  sX_ep_name <- url2 %>% 
    html_nodes(".info a") %>% 
    html_text() %>% 
    as_tibble() %>% 
    mutate(value = gsub("\\n", "", x = value))
  
  # Grab episode rating
  sX_rate <- url2 %>% 
    html_nodes(".ipl-rating-widget > .ipl-rating-star .ipl-rating-star__rating") %>% 
    html_text() %>% 
    as_tibble() %>%  
    mutate(rating = gsub("\\n", "", x = value) %>% as.numeric) %>% 
    select(-value)
  
  # Clean episode name df
  sX_ep_name <- sX_ep_name %>% 
    mutate(title = trimws(value)) %>% 
    filter(!str_detect(title, "Rate"), title != "") %>% 
    select(-value)
  
  # combine name + rating
  ep_rating <- sX_ep_name %>% 
    bind_cols(sX_rate)
}

ep_rating_df <- map2(.x = url_df$urls, .y = url_df$season_num,
                          ~ brooklyn99_ep_rating(url = .x) %>% 
         mutate(season = .y)) %>% 
  reduce(bind_rows)

ep_rating_df <- ep_rating_df %>% 
  group_by(season) %>% 
  mutate(ep_num = row_number()) %>% 
  ungroup()

glimpse(ep_rating_df)
```

OK, looks good.

## Episode Ratings Plot: Heatmap and Boxplot

I used `geom_tile()` to create a heat map of episode ratings with the season number as the rows and the episode number for that season as the columns. I used the `dichromat` package for the color scheme "LightBluetoDarkBlue.10", it meshes pretty well with the _Brooklyn 99_ color theme!

```{r fig.height=5, fig.width=7}
rating_plot <- ep_rating_df %>% 
  ggplot(aes(x = ep_num, y = season)) +
  geom_tile(aes(fill = rating), size = 1.5,
            color = "black") +
  scale_fill_gradientn("Rating", colors = dichromat::colorschemes$LightBluetoDarkBlue.10,
                       breaks = c(7.7, 8, 8.5, 9, 9.5)) +
  guides(fill = guide_colourbar(frame.colour = "black",
                                barwidth = unit(2, "in"))) +
  scale_x_continuous(expand = c(0.01, 0.01), 
                     breaks = c(1, seq(from = 5, to = 20, by = 5), 23),
                     labels = c(1, seq(from = 5, to = 20, by = 5), 23)) +
  scale_y_reverse(expand = c(0.01, 0.01),
                  breaks = c(1:7), 
                  labels = c(1:7)) +
  labs(x = "Episode Number", y = "Season",
       title = "Episode Ratings") +
  theme_b99() +
  theme(panel.grid = element_blank())

rating_plot
```

From what we can see on the graph there doesn't seem to be any trends along either axes besides the fact that the finales and the subsequent opening episode of the following season are generally well-received. Two stand out episodes from __Season 5__ can be clearly seen in the plot. These episodes are "HalloVeen" (the fifth Halloween episode of the series)  and "The Box" (an excellent episode featuring __Sterling K. Brown__ as the perp). 

## Box Plot

Another way to visualize this would be with the box plot. This way allows you to make a comparison between seasons, whereas the heat map could be used to pick out any trends over time or sequence.

The debate between violin plot vs. box plot vs. sina plot vs. etc. rages on to this day (some examples I've read over the years: [1](https://cerebralmastication.com/2009/02/box-plot-vs-violin-plot-in-r/), [2](https://simplystatistics.org/2017/07/13/the-joy-of-no-more-violin-plots/), [3](https://rpubs.com/crazyhottommy/sina-plot)) and some of the arguments made seem to come down to personal preference. Since the data I'm using is quite small (~20 episode ratings for each season), in my case it might be better to use box plots (instead of violin plots) and sprinkle bee swarm points on top with the [ggbeeswarm](https://github.com/eclarke/ggbeeswarm) package. I commented out some of the other methods if you wanted to copy-paste this code chunk into your R console to try them out!

I highlighted the outliers for each season in red with the unintentional result being that the color scheme mimics that of the flag of Colorado...

```{r fig.height=5, fig.width=7}
cols <- c("1" = "#6CA9C3", "2" = "#3A3533", 
          "3" = "#000E33", "4" = "#CBCFD2", "5" = "#175E78")

box_plot <- ep_rating_df %>% 
  ggplot(aes(x = season, y = rating, group = season)) +
  #geom_violin(color = "#F9FEFF", fill = "#000E33") +
  #ggthemes::geom_tufteboxplot(color = "#F9FEFF", fill = "#000E33") +
  #ggforce::geom_sina(color = "#F9FEFF", fill = "#000E33") +
  geom_boxplot(color = "#F9FEFF", fill = "#000E33",
              outlier.color = "red", outlier.size = 5) +
  geom_beeswarm(color = "#FCF40E", cex = 2, size = 2.25) +
  scale_y_continuous(limits = c(7.5, 9.6),
                     labels = c(7.5, 8, 8.5, 9, 9.5)) +
  labs(title = "Episode Ratings by Season",
       x = "Season", y = "Rating") +
  theme_b99() +
  theme(panel.grid.minor = element_blank())

box_plot
```

Noice, Smort! We get the best of both worlds by combining two different types of visualizing distributions. Let's check out which episodes those red dots are...

```{r}
ep_rating_df %>% 
  group_by(season) %>% 
  mutate(n = n(),
         third_quantile = quantile(rating)[4]) %>% 
  filter(rating > third_quantile + 1.58 * (IQR(rating))) %>% 
  select(-n, -third_quantile)
```

Besides the (re)appearances of Doug Judy, _Brooklyn Nine-Nine_ is known for its Halloween Episodes. I wanted to use `gt` somewhere in this blog post but that's little bit overkill so a `kable` table will suffice for now.

```{r}
ep_rating_df %>% 
  group_by(season) %>% 
  top_n(n = 5, wt = rating) %>% 
  arrange(desc(rating)) %>% 
  mutate(rank = row_number()) %>% 
  arrange(season, desc(rating)) %>% 
  filter(str_detect(title, "Hallo")) %>% 
  rename(Title = title, Rating = rating, Season = season,
         `Episode Number` = ep_num, Rank = rank) %>% 
  kable(format = "html",
        caption = "The Halloween Episodes and Rank in Season") %>% 
  kable_styling(full_width = FALSE)
```

It is very clear that the Halloween episodes are highly regarded to those that rate _Brooklyn Nine-Nine_ on IMDB (although I'm sure most fans including myself will agree).

<center>
<img src = "https://78.media.tumblr.com/5fd58d43ff6eeb965c9d623d783f31eb/tumblr_oy44wkivKi1vj8gn9o1_540.gif" width = "450" />
</center>

A more recent variant for showing a distribution is the ridge-line plot, courtesy of the [ggridges](https://github.com/clauswilke/ggridges) package:

```{r fig.height=5, fig.width=7}
ep_rating_df2 <- ep_rating_df %>% 
  mutate(season = as_factor(as.character(season)))

ep_rating_df2 %>% 
  ggplot(aes(x = rating, y = season, height = ..density..)) +
  ggridges::geom_density_ridges(color = "#F9FEFF", fill = "#000E33") +
  labs(title = "Episode Ratings by Season",
       x = "Rating", y = "Season") +
  scale_x_continuous(limits = c(7.25, 9.8),
                     breaks = c(7.5, 8, 8.5, 9, 9.5),
                     labels = c(7.5, 8, 8.5, 9, 9.5)) +
  scale_y_discrete(limits = rev(levels(ep_rating_df2$season))) +
  theme_b99() +
  theme(panel.grid.minor = element_blank())
```

<center>
<img src = "https://media.giphy.com/media/8PQOq6nMYO0kU/giphy.gif" width = "450" />
</center>

Well OK, we're just looking at distributions... but I wanted to use this GIF in some capacity!

# Cast Appearances

The main cast of _Brooklyn Nine-Nine_ are pretty tightly knit and as members of the same precinct it makes sense that they'll generally appear together. So instead, I wanted to look at which non-main cast members and guests made the most appearances on the show. __Special note__: Hitchcock and Scully weren't officially "main cast" until __Season 2__ but I left them out of the non-main cast list. After scraping for the full cast list and main cast list, I `anti_join()` them so I am left with the non-main cast and the number of episodes that they appeared in.

```{r warning=FALSE, message=FALSE}
# Entire cast:
cast_url <- bow("https://www.imdb.com/title/tt2467372/fullcredits?ref_=tt_cl_sm#cast")

cast_info_raw <- scrape(cast_url) %>% 
  html_nodes(".character") %>% 
  html_text() %>% 
  as_tibble()

cast_info_clean <- cast_info_raw %>% 
  separate(value, into = c("blank", "name", "episode_num", "dots"), sep = "\n") %>% 
  mutate(episode_num = case_when(
    episode_num == "         / ...  " ~ dots,
    TRUE ~ episode_num),
    episode_num = episode_num %>% word(., 1, sep = "e") %>% as.numeric,
    name = str_trim(name, side = "both")) %>% 
  select(-blank, -dots) %>% 
  mutate(name = case_when(
    name == "Captain Ray Holt" ~ "Ray Holt",
    name == "Scully" ~ "Norm Scully",
    name == "Hitchcock" ~ "Michael Hitchcock",
    name == "Deputy Chief Madeline Wuntch" ~ "Madeline Wuntch",
    TRUE ~ name))
  
# Main cast:
cast_main_url <- bow("https://en.wikipedia.org/wiki/List_of_Brooklyn_Nine-Nine_characters")

cast_main_raw <- scrape(cast_main_url) %>% 
  html_nodes(".wikitable") %>% 
  html_table(fill = TRUE) %>% 
  flatten_df() %>% 
  as_tibble()

cast_main_clean <- cast_main_raw %>% 
  slice(-1) %>% 
  select(Character)

# anti-join
non_main_cast <- anti_join(cast_info_clean, cast_main_clean, 
                           by = c("name" = "Character"))
```

## Non-Main Cast Appearances Plot

To shorten the list I'll just look at the top five cast members. I create a "halfway" variable so that the number labels will appear right in the middle of each bar. Using the `axis_canvas()`, `draw_image()`, and `insert_axis_grob()` from the `cowplot` package I can insert images of the characters along the bottom of the plot.

```{r fig.height = 6, fig.width = 10}
non_main_plot <- non_main_cast %>% 
  arrange(desc(episode_num)) %>% 
  head(5) %>% 
  mutate(halfway = episode_num / 2) %>% 
  ggplot(aes(x = reorder(name, desc(episode_num)), y = episode_num)) +
  geom_col(fill = "#000E33") +
  geom_text(aes(y = halfway, label = episode_num,
                family = "Univers"),
            color = "#F9FEFF",
            size = 8) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 12.5),
                     breaks = c(2, 4, 6, 8, 10, 12),
                     labels = c(2, 4, 6, 8, 10, 12)) +
  labs(title = "Most Appearances by Non-Main Cast", 
       x = NULL, y = "Number of Episodes") +
  theme_b99() +
  theme(panel.grid.major.x = element_blank())

# images
pimage <- axis_canvas(non_main_plot, axis = 'x') + 
  draw_image(
    "https://vignette.wikia.nocookie.net/tvdatabase/images/d/d5/Adrian_Pimento.jpg", 
    x = 0.5, scale = 1.3, clip = "on") +
  draw_image(
    "https://vignette.wikia.nocookie.net/brooklynnine-nine/images/a/ab/Kevin.jpg", 
    x = 1.5, scale = 1.3, clip = "on") +
  draw_image(
    "https://vignette.wikia.nocookie.net/brooklynnine-nine/images/b/b3/Wuntch.png", 
    x = 2.5, scale = 1.3, clip = "on") +
  draw_image(
    "https://vignette.wikia.nocookie.net/brooklynnine-nine/images/0/0a/Doug_Judy.png",
    x = 3.5, scale = 1.3, clip = "on") +
  draw_image(
    "https://vignette.wikia.nocookie.net/brooklynnine-nine/images/2/23/Vulture.jpg",
    x = 4.5, scale = 1.3, clip = "on")

# insert the image strip into the bar plot and draw  
ncast_plot <- ggdraw(insert_xaxis_grob(non_main_plot, pimage, position = "bottom"))

ncast_plot
```

Adrian has appeared in the most episodes just beating out Kevin. This really shows how involved Adrian was in the story in __Season 4__ and __5__ especially compared to Kevin who has been popping in and out since the first season. Everybody's favorite __DOUG JUDY__ rounds off this bar chart next to The Vulture.

<center>
<img src = "https://66.media.tumblr.com/87972a8335ae460091c2005ff519f009/tumblr_omcy241y071w4nkyqo4_400.gif" width = "450" />
</center>

# Viewer Numbers

Pretty much the same M.O. as what I did to get the episode ratings here. One thing of note was using regex to get rid of the footnotes. I had to be careful to double escape the square brackets there.

```{r}
url_wiki_df <- tibble(
  urls = c("https://en.wikipedia.org/wiki/Brooklyn_Nine-Nine_(season_1)",
           "https://en.wikipedia.org/wiki/Brooklyn_Nine-Nine_(season_2)",
           "https://en.wikipedia.org/wiki/Brooklyn_Nine-Nine_(season_3)",
           "https://en.wikipedia.org/wiki/Brooklyn_Nine-Nine_(season_4)",
           "https://en.wikipedia.org/wiki/Brooklyn_Nine-Nine_(season_5)"),
  season_num = c(1, 2, 3, 4, 5))

brooklyn99_ep_info <- function(url) {
  
  session <- bow(url)
  
  episode_raw <- scrape(session) %>% 
    html_nodes(".wikiepisodetable") %>% 
    html_table(fill = TRUE) %>% 
    flatten_df() %>% 
    as_tibble() %>% 
    filter(row_number() %% 2 != 0)
  
  episode_table <- episode_raw %>% 
  set_names(c("num_overall", "num_season", "title", "director", "writer",
              "air_date", "prod_code", "viewers")) %>% 
  mutate(viewers = str_remove_all(viewers, "\\[[0-9]+\\]") %>% as.numeric)
  
}

ep_info_df <- map2(.x = url_wiki_df$urls, .y = url_wiki_df$season_num,
                          ~ brooklyn99_ep_info(url = .x) %>% 
         mutate(season = .y)) %>% 
  reduce(rbind)

ep_info_df %>% 
  slice(77:83)
```

## tidylog Demonstration

A little intermission here as I wanted to talk about this cool package I recently found on Twitter called [tidylog](https://github.com/elbersb/tidylog). To show you an example, I will take a look at which writers wrote the most episodes in __Season 5__:

```{r, warning=FALSE}
library(tidylog)

ep_info_df %>% 
  select(season, num_season, title, num_overall, writer, viewers) %>% 
  filter(season == 5) %>% 
  separate_rows(writer, sep = "&") %>% 
  mutate(writer = writer %>% trimws) %>% 
  group_by(writer) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>% 
  head(5)
```

You can see that it gives you details on what each `dplyr` function changed in your data frame in the order that the operations were performed. It's pretty cool and it gets more useful as your `dplyr` pipeline grows longer! However, let's turn `tidylog` off for now:

```{r}
options("tidylog.display" = list())
```

The episode info data frame we got from Wikipedia had a lot of information so let's chop it down a bit to get data on the number of viewers per episode.

From what we saw of `ep_info_df` earlier, the data looked pretty clean already except for "The Fugitive" episodes being formatted differently... 

<center>
<img src = "https://66.media.tumblr.com/cc01463acbe445711497b5c979b996d1/tumblr_ov5bc3udjC1ty7lb2o1_540.gif" width = "450" />
</center>

There are other multi-part episodes throughout the show but this pair is the only one that aired on the same day, on New Years Day 2017, so they got smushed together in the Wikipedia table when we scraped it. There wasn't a quick and easy way to `regex` them into separate rows so I just filtered them out and added them back in. Then at the end of the pipe, I create a `first` and `last` variable for each season taking note of what overall episode number the first and last episodes of each season were. You'll see why I did this soon.

```{r fig.height = 4, fig.width = 10}
viewers_df <- ep_info_df %>% 
  select(season, num_season, title, num_overall, viewers) %>% 
  # manually fix "The Fugitive" episodes
  filter(num_overall != 7980) %>% 
  add_row(season = 4, num_season = 11, title = "The Fugitive: Part 1", 
          num_overall = 79, viewers = 3.49) %>% 
  add_row(season = 4, num_season = 12, title = "The Fugitive: Part 2", 
          num_overall = 80, viewers = 3.49) %>% 
  mutate(num_overall = as.numeric(num_overall),
         num_season = as.numeric(num_season),
         season = as_factor(as.character(season))) %>% 
  arrange(num_overall) %>% 
  group_by(season) %>% 
  mutate(first = first(num_overall),
         last = last(num_overall)) %>% 
  ungroup() 
```

## Viewers Plot

For this plot I use `geom_rect()` to give a colored background for each season. I set the span of the Xs as the `first` and `last` episode number of each season for the width and using `Inf` and `-Inf` for the Ys to cover the entire height of the plot. For the season labels I calculated the midpoint along the x-axis for each season and used that as the x values (not shown in the code). I could have used facets but to the best of my knowledge I wouldn't have been able to place the labels on top across multiple facets anyways. It may be possible by placing text grobs on top of the facetted plot but I thought that would take more time compared to what I did with `geom_rect()`. Otherwise I use a lot of `annotate()` code to add in the episode details and season titles.

```{r fig.height = 6, fig.width = 11}
# Color hex codes for season blocks:
cols <- c("1" = "#6CA9C3", "2" = "#3A3533", 
          "3" = "#000E33", "4" = "#CBCFD2", "5" = "#175E78")

viewer_plot <- viewers_df %>% 
  ggplot(aes(x = num_overall, y = viewers, group = season)) +
  geom_rect(aes(xmin = first, xmax = last,
                fill = season), alpha = 0.2,
            ymin = -Inf, ymax = Inf) +
  geom_line(color = "white", size = 1.1) +
  scale_fill_manual("Season", values = cols, guide = FALSE) +
  scale_y_continuous(limits = c(0, 20),
                     breaks = c(seq(0, 15, by = 2.5)),
                     expand = c(0, 0)) +
  scale_x_continuous(breaks = c(seq(0, 112, by = 5)),
                     labels = c(seq(0, 112, by = 5)),
                     expand = c(0, 0)) +
  labs(x = "Episode Number (Overall)", y = "Viewers (Millions)",
       title = "Viewers by Episode") +
  theme_b99() +
  theme(panel.grid = element_blank()) +
  # Line segments
  annotate(geom = "segment", x = 15, xend = 15, y = 15, yend = 16., 
           color = "black", size = 1.2) +
  annotate(geom = "segment", x = 34, xend = 34, y = 6, yend = 7, 
           color = "black", size = 1.2) +
  annotate(geom = "segment", x = 79.5, xend = 79.5, y = 3.5, yend = 5, 
           color = "black", size = 1.2) +
  # Episode details
  annotate(geom = "label", x = 7, y = 16.5, hjust = 0, size = 4.5,
           family = "Univers",
           label = "Operation: Broken Feather (Aired after Super Bowl XLVIII)") +
  annotate(geom = "label", x = 25, y = 7.5, hjust = 0, size = 4.5, 
           family = "Univers",
           label = "Beach House (Sunday before First Workday of 2015)") +
  annotate(geom = "label", x = 67, y = 5, hjust = 0, size = 4.5,
           family = "Univers",
           label = "The Fugitive: Part 1 & 2 (New Years Day 2017)") +
  # Season titles
  annotate(geom = "label", x = 11.5, y = 19, size = 7,
           family = "Univers",
           label = "Season One") +
  annotate(geom = "label", x = 34, y = 19, size = 7,
           family = "Univers",
           label = "Season Two") +
  annotate(geom = "label", x = 57, y = 19, size = 7,
           family = "Univers",
           label = "Season Three") +
  annotate(geom = "label", x = 79.5, y = 19, size = 7,
           family = "Univers",
           label = "Season Four") +
  annotate(geom = "label", x = 102, y = 19, size = 7,
           family = "Univers",
           label = "Season Five") 

viewer_plot
```

I added in details on why certain episodes had such high viewership compared to others from both my memory and a little digging but I wasn't really sure about those three peaks in __Season 3__. One of them was a **Halloween** episode (which is up there with the **Pontiac Bandit** episodes for the best recurring episodes), but in terms of the actual airing dates I can't quite remember anything significant happening on those days that would explain the high viewer numbers (relative to the other episodes in the season).

Throughout it's run on FOX, the show averaged around 2~3.5 million viewers with numerous peaks and troughs until the 5th season where it only averaged around 1.8 million viewers but kept those numbers very consistently across the entire season.

# Creating the Title Card

The last thing I want to do to wrap up this blog post is to create an infographic containing the plots I made above. Before I combine them all I want to make a title card that looks similar to the official Brooklyn Nine-Nine title card you see at the beginning of the episode. 
Here's what it looks like:

<center>
<img src = "https://upload.wikimedia.org/wikipedia/commons/thumb/8/8d/Brooklyn_nine-nine_logo.png/800px-Brooklyn_nine-nine_logo.png" width = "450" />
</center>

Now I could just paste the `URL` for the picture into my graph but I thought why not try making it myself? So, I used `geom_polygon()` to construct the two diagonal colored bars and then placed the text on top of them with `annotate()`. 

```{r fig.width = 16, fig.height = 5.5}
rect <- data.frame(id = as.factor(c(1, 1, 1, 1,
                          2, 2, 2, 2)),
                   x = c(16, 16, 0,    0,
                         16, 16, 6.6,  6.5),
                   y = c(5.1, 2, 0.4,  3.5,
                         2.5, 0.8, 0,  1.6))

header <- ggplot(data = rect, aes(x, y, group = id, fill = id)) +
  geom_polygon() +
  scale_fill_manual(values = c("#0053CD", "#000E33"), guide = FALSE) +
  annotate(geom = "text", y = 2, x = 1.8, hjust = 0,
           family = "Univers LT 93 ExtraBlackEx", 
           color = "#fcf7e8", size = 40, angle = 5,
           label = glue("
                        BROOKLYN")) +
  annotate(geom = "text", y = 0.9, x = 7.2, hjust = 0,
           family = "Univers", 
           color = "#fcf7e8", size = 28, angle = 3.5,
           label = glue("
                        NINE-NINE")) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 16)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 5.5)) +
  theme_void() +
  theme(plot.background = element_rect(color = "#F9FEFF", 
                                       fill = "#F9FEFF", 
                                       size = 8))

header
```

<center>
<img src = "https://media.tenor.com/images/098e4852dfdc41991add5983e9262a92/tenor.gif" width = "200" />
</center>

After going through this process (read:time-consuming ordeal) I don't recommend making stuff like this manually as it can be quite frustrating especially if you have to get it to fit alongside other plots and grobs!

Finally, let me just add a footer:

```{r fig.width=16, fig.height = 1}
foot <- ggplot() + 
 annotate(geom = "text", x = 12.5, y = 0.5,
          size = 4, family = "Univers", color = 'white', hjust = 0,
          label= glue("
                      Source: Wikipedia, Nielsen Ratings, IMDB
                      By @R_by_Ryo")) + 
  lims(x = c(0, 16), y = c(0, 1)) +
  theme_b99() +
  theme(panel.grid = element_blank(),
        text = element_blank())

foot
```


## Arrange Plots with cowplot

With all the components done, now I just need to arrange all of the plots, the title card, and the footer together to create the _Brooklyn Nine-Nine_ infographic!

There are several ways to do this like using `grid.arrange()` from the `grid` package or the newer `patchwork` package but I went for `cowplot::plot_grid()` this time.

```{r fig.height=12, fig.width=16, dpi = 108}
the_nine_nine_plot <- plot_grid(
  plot_grid(header),
  plot_grid(viewer_plot),
  plot_grid(box_plot, ncast_plot,
            rel_widths = c(3, 4)),
  plot_grid(foot),
  ncol = 1, rel_heights = c(1, 1, 1, 0.25))

the_nine_nine_plot
```

<center>
<img src = "https://media2.giphy.com/media/l4JySAWfMaY7w88sU/source.gif" width = "450" />
</center>

# Conclusion

In this blog post I went over creating your own custom `ggplot2` theme, web scraping, cleaning and tidying data frames with the `tidyverse`, and creating a variety of plots to show simple statistics on _Brooklyn Nine-Nine_. You can check out all the code in this [GitHub Repo](https://github.com/Ryo-N7/brooklyn_NINE_NINE_viz).

The plots were pretty simple so the main problems I had were in sizing and scaling stuff properly. I feel like some of it is still not perfect but it's good enough for now. This is an area I feel like I need to improve on and find ways to automatically scale things using `magick` or custom functions. This was also my first time using a different color scheme for my plots, usually I just slap `theme_minimal()` to most things and call it a day. It took me a while to get the color coordination right and I think I got it to a level where it isn't nauseating to look at! 

To conclude I just wanted to list out my top five __"Cold Opens"__ (in no particular order):

- [Halloween Boyle](https://www.youtube.com/watch?v=RzWSM-liu4I)
- [THE FULL BULL PEN](https://www.youtube.com/watch?v=lFqqXYVdrUs)
- [Amy is late to work](https://www.youtube.com/watch?v=EQ6HaIP5uwg)
- [Holt's new hat](https://www.youtube.com/watch?v=rxZBW8Pfklc)
- [Boyle's weekend](https://youtu.be/O9gg0pz7rlc?t=404)

Agree? Disagree? Let me know in the comments below!

I hope you had as much fun reading this as I did making it. If you didn't, then well...

<center>
<img src = "https://66.media.tumblr.com/c0584c949c88744289b97aecd7186eba/tumblr_osdftshJze1ukq7ljo4_400.gif" width = "450" />
</center>